### 2022-01-11 paper/paper.tex

Julia does not perform automatic fused multiply-add (FMA) contraction, that is
replacing a multiplication followed by an addition with a single FMA instruction,
as it is inconsistent with its strict floating point semantics.
In other compilers, this optimization is controlled by a global compiler option
(\lstinline{-ffp-contract} in GCC and Clang) and often enabled at reasonable
optimization levels such as \lstinline{-O2} for GCC and Intel compilers\footnote{%
An interesting coincidence is that not only Julia but most LLVM-based frontends
tend not to enable FMA contraction by default.}.
In Julia, FMA contraction is controlled more locally: the
\lstinline{muladd}%\footnote{\url{https://docs.julialang.org/en/v1/base/math/\#Base.muladd}}
intrinsic function allows the compiler to evaluate a multiply-add using the most
efficient method. Relying on Julia's code manipulation techniques, the
\lstinline{@muladd}%\footnote{\url{https://github.com/SciML/MuladdMacro.jl}}
macro makes it convenient to use the \lstinline{muladd} function by
syntactically rewriting expressions to insert \lstinline{muladd} in appropriate
locations.

>>>>

Julia does not perform automatic fused multiply-add (FMA) contraction, i.e.,
replacing a multiplication followed by an addition with a single FMA instruction,
as it is inconsistent with its strict floating point semantics.
In other compilers, this optimization can be controlled by a global compiler option
(\lstinline{-ffp-contract} in GCC and Clang) and is often enabled at reasonable
optimization levels such as \lstinline{-O2} for GCC and Intel compilers\footnote{%
An interesting coincidence is that not only Julia but most LLVM-based frontends
tend not to enable FMA contraction by default.}.
In Julia, FMA contraction is controlled more locally: the
\lstinline{muladd} %\footnote{\url{https://docs.julialang.org/en/v1/base/math/\#Base.muladd}}
intrinsic function allows the compiler to evaluate a multiply-add using the most
efficient method. Relying on Julia's code manipulation techniques, the
\lstinline{@muladd} %\footnote{\url{https://github.com/SciML/MuladdMacro.jl}}
macro makes it convenient to use the \lstinline{muladd} function by
syntactically rewriting expressions to insert \lstinline{muladd} in appropriate
locations.
